%https://tex.stackexchange.com/questions/114219/add-notes-to-latex-beamer
\documentclass[14pt, aspectratio=169]{beamer}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{dsfont}
\usepackage{multicol}
\usepackage{multirow}
% \usepackage{pgfpages}
% \setbeameroption{show notes}
%\setbeameroption{hide notes} % Only slides
%\setbeameroption{show only notes} % Only notes
% \setbeameroption{show notes on second screen=right} % Both
%% USAGE: 
% \usepackage[logo="sklogo.png"]{beamerskoltech} 
%   if you have a stand-alone image file for Sk logo 
% or
% \usepackage[logo]{beamerskoltech} 
%   if you has no logo-file, but want LaTeX to generate it. 
%   In this case you probably will need to use `--enable-write18 -interaction=nonstopmode` arguments running the latex command.
%   in papeeria and overleaf all works fine
% or 
% \usepackage{beamerskoltech}
%   In case you don't want logo at all 
%
% provided commands:
% color `skoltechgreen` -- the dark-green color for structure elements 
% command `\logoname` -- the name of logo file if exist 
% command `{\csk <text>}` -- the shortcut from `\color{skoltechgreen}`
% command `skfootnote{text}` -- put some text for current slide
% `\renewcommand{\skbeforetitle}{\vspace{-3ex}}` is useful in case you use `aspectratio=169`
%%%%%%%%%%%%%%%%
\usepackage[logo]{beamerskoltech} 
\usepackage{lecturessk}
\renewcommand{\skbeforetitle}{\vspace{-3ex}}

\usepackage{xecyr}
\usepackage{hyperref}

\usepackage{polyglossia}
\usepackage{graphicx}
\usepackage{listings}



\begin{document}


\title{\LaTeX:\\ \Large from dummy to \TeX nician}
\subtitle{Create articles, presentations, posters}
\author{David Saykin \& Anton Lioznov}
\institute{Skoltech}
\date{ISP 2019,\\ \textit{lesson 2}}
\frame{\titlepage}
\begin{frame}\frametitle{What we will know?}
\tableofcontents[hideallsubsections]
\end{frame}
\begin{frame}{Acknowledgments}\relax
We acknowledge 
\begin{description}
    \item[Vlad Yurchenko] for beeing co-author of the first version of this presentation in 2015 
    \item[Dmitry Barashev] for useful comments, that was included in the presentation
    \item[Alexander Kulikov] for useful comments, that was included in the presentation
\end{description}
\end{frame}

\begin{frame}{Agreements}{I}\relax
{ \Large Footnotes }
\smash{
\raisebox{-5.4cm}{
\begin{tikzpicture}
\draw[white] (0,0) -- (0, 0.0);
\draw[->,ultra thick] (0,0) to[out=0,in=45] (8, -1.5) -- (4,-5.5);
\end{tikzpicture}}
}

\skfootnote{Like this}
\begin{itemize}
    \item Only in the ``out-class'' version
     \item For second reading
     \item Containe advanced usage of the command 
     \item Containe references to read more 
     \begin{itemize}
         \item to the exact chapter 
         \item (often) with the href to exact page  
     \end{itemize}
     \item Containe some comments 
\end{itemize}
\end{frame}

%\renewcommand{\skfootnote}[1]{}

\begin{frame}{Agreements}{II}\relax
{ \Large Addition information -- ``magic'' } 
\smash{\begin{tikzpicture}
\draw[white] (0,0) -- (0, 0.6);
\draw[->,ultra thick] (0,0.3) --(3,1.8);
\end{tikzpicture}}
\magicPage

\begin{itemize}
     \item To have the full picture 
     \item Not to analyze or to puzzle out in class 
\end{itemize}
\end{frame}

\inclassFrame{
\begin{frame}{Agreements}{III}\relax
\centering
     {\LARGE This slide means it is ``in-class task time''\par
     \inclassFrag{This box means it is ``in-class task time''}}
     These slides and boxes will be removed in the ``out-class'' version. However, they still be in the source code. 
\end{frame}
}

\AtBeginSection[] 
{
  \begin{frame}{What we will know?}
  \tableofcontents[currentsection,hideallsubsections]
  \end{frame}
}

\AtBeginSubsection[]
{
  \begin{frame}{What we will know?}
  \tableofcontents[currentsubsection, hideothersubsections, sectionstyle=show/hide, subsectionstyle=show/shaded/hide]
  \end{frame}
}

\section{Document Creation}

\input{sec01/sec01}

\section{Presentation Creation}

\input{sec02/sec02}

\begin{frame}\frametitle{What we have learned today?}
\tableofcontents
\end{frame}


\begin{frame}[allowframebreaks]{references}
color from the footnotes corresponds to references' color.
    \begin{itemize}
        \item \knuthc{Knuth ``The \TeX Book''}
        \item \lvoc{L'vovsky ``Nabor i verstka v sisteme \LaTeX''}
        \item \lamc{Lamport. ``\LaTeX. A Document Preparation System, User’s Guide and Reference Manual''}
        \item \lmanc{``\LaTeX 2e: An unofficial reference manual''} also at website \url{https://latexref.xyz/}
        \item \stExC{https://tex.stackexchange.com/questions} : \url{https://tex.stackexchange.com/questions}
        \item \wikiC{https://en.wikibooks.org/wiki/LaTeX} : \url{https://en.wikibooks.org/wiki/LaTeX}
        \item \overC{https://www.overleaf.com/learn/latex} : \url{https://www.overleaf.com/learn/latex}
        \item \tugC{https://www.tug.org/utilities/plain/cseq.html} : \url{https://www.tug.org/utilities/plain/cseq.html}
    \end{itemize}
\end{frame}

\begin{frame}{Distribution}\relax
\begin{itemize}
     \item the pdf-version of the presentation and all printed materials can be distributed under license Creative Commons Attribution-ShareAlike 4.0 \url{https://creativecommons.org/licenses/by-sa/4.0/}
     \item The source code of the presentation is available on {\csk\url{https://github.com/Lavton/latexLectures}} and can be distributed under the MIT license \url{https://en.wikipedia.org/wiki/MIT_License\#License_terms}
\end{itemize}
     
\end{frame}
\end{document}