\documentclass{article}
\usepackage{coffee}
% \usepackage{geometry}
% \geometry{paperwidth=150mm, paperheight=150mm, left=5mm, top=5mm, right=5mm, bottom=5mm}
\begin{document}
\title{LaTeX Coffee Stains}
\author{Hanno Rein\\
\texttt{http://hanno-rein.de}\\
Cambridge University}
\renewcommand{\today}{April 3, 2009}
\maketitle
\coffee[0.4pt]{1}
\section{Introduction}
This package provides an essential feature to \LaTeX~that has been missing for too long. It adds a coffee stain to your documents. A lot of time can be saved by printing stains directly on the page rather than adding it manually. You can choose from four different stain types:
\begin{enumerate}
  \item $270^\circ$ circle stain with two tiny splashes 
  \item $60^\circ$ circle stain 
  \item two splashes with light colours
  \item and a colourful twin splash.
\end{enumerate}

\section{Usage}
To use the package, simply place the \texttt{coffee.sty} file in the directory with all of your other \texttt{.tex} files \textit{or} install it properly (consult your distribution's manual). Then include the following line in the header of your document:
\begin{verbatim}
\usepackage{coffee}
\end{verbatim}
To place a coffee stain on a page, put one of the following commands in the source code of the relevant page: 
\begin{verbatim}
\coffee{1} % stain 1 (see this page)
\coffee{2} % stain 2 (see next page)
\coffee{3} % stain 3 (see page 3)
\coffee{4} % stain 4
\end{verbatim}
The package requires \texttt{eso-pic}, \texttt{ifthen} and \texttt{pstricks}. Currently it does not work with \texttt{pdflatex}. Sorry about that. If you know how to change this, let me know.  
\newpage
\noindent You can adjust the size of the stains as follows:
\begin{verbatim}
\coffee[0.3pt]{1}  %small stain
\coffee[0.7pt]{1}  %large stain
\end{verbatim}
If you want to change the position of the stains on the page you have to do some hacking. Have a look at the end of the \texttt{coffee.sty} file. It shouldn't be very hard. 

\section{Copyright}
You can freely distribute this package as I do not believe in imaginary property. All stains are self-made, photographed by myself, processed with gimp and traced with Inkscape.
Donations should be made in coffee only. My address is
\begin{quote}
Hanno Rein\\
DAMTP, CMS\\
Wilberforce Road\\
Cambridge CB3 0WA\\
United Kingdom
\end{quote}
See more coffee stains on the next pages.
\coffee{2}
\newpage
\coffee{3}
Coffee is great.
\newpage
\coffee[0.1pt]{4}
Coffee will save the world. 
\end{document}
